Comparing software variability across and within fMRI analysis packages

### 2021-12-23 paper/paper.tex
A pass on intro-methods-results

\title{Comparing variability across and within fMRI analysis software packages}

@@

\maketitle
\begin{abstract}
  Variability has been broadly observed in functional MRI analyses as a result of differences
  both between and within analytic tools. However, the
  relationship between within-tool and between-tool variabilities for a
  given analysis is unclear. We extended a previous comparison of fMRI
  analysis software libraries (namely FSL, AFNI, and SPM) and related the
  observed differences to within-tool variability
  simulated using Monte-Carlo arithmetic. In group analyses, we found that
  between-tool variability was consistently larger than within-tool
  variability simulated from numerical perturbations of the magnitude of
  machine error. In subject analyses, the same within-tool variability
  approached between-tool variability in some regions for some subjects.
  Interestingly, within- and between-tool variabilities appeared moderately
  correlated ($r > 0.5$) in all tested conditions. Finally, we found that
  within-tool variability had effects of similar magnitude to between-tool
  variability when simulated from numerical perturbations introduced at the virtual
  precision of 17 bits --- a high but plausible level of uncertainty for
  scientific computing libraries \gk{What does this mean? They only have
  precision of 17, or they use data that is 17 bits?}.
   \yohan{agree with Greg, it is unclear and a strong assertion!}
   \camille{It is not entirely clear to me how this relates to the previous
   conclusions that BT variability was consistently larger than machine
   error} \tristan{Better?} Our findings motivate the
  continued investigation of within-tool variability in neuroimaging, and position it
  as a possible proxy for studying arbitrary between-tool variations.
\end{abstract}

@@

Recent explorations of the analytical flexibility in brain imaging across
tools, platforms, or teams, have demonstrated unexpected variability in
results, even when analyzing identical data~\cite{botvinik2020variability}. Possible explanations for
such discrepancies include methodological flexibility~\cite{carp2012plurality} and software
variability, the focus of this paper. A recommendation to address this
variability is to adopt a ``multiverse" approach that analyzes the same
dataset multiple times in different software environments, and ultimately
conclude from the resulting set of outcomes. However, the range of
analytical conditions to be included in such multiverse analyses remains
poorly defined, both because of the boundless set of tools and
configurations, and that the precise causes of software variability remain
unclear. This lack of clarity is in part because fMRI analyses depend on
complex software stacks that leverage low-level libraries provided by the
operating system (e.g.,mathematical functions), general scientific
computing methods (e.g., optimization toolboxes), and specific fMRI
analysis tools (e.g., spatial image normalization methods). At each level,
conceptual and implementation differences across experiments may each
create substantial variability in the analysis outcomes.

As a result of these factors, the variability resulting from the use of
different fMRI analysis tools implementing similar analytical approaches
(between-tool variability) can reach worrying magnitudes. For instance, the
study in~\cite{bowring2019exploring} compared the results produced by the
three main fMRI analysis toolboxes, namely SPM~\cite{penny2011statistical},
AFNI~\cite{cox1996afni} and FSL~\cite{jenkinson2012fsl}, using similar
pipelines. It reported limited similarity between the activation clusters
produced by these tools, measured by Dice coefficients ranging from 0.0 to
0.769, where 0 indicates non-overlapping
clusters and 1 means identical clusters. More recently, the work
in~\cite{Li2021.12.01.470790} also showed a low similarity between the
results produced by five different tools (ABCD~\cite{feczko2021adolescent},
CCS~\cite{xu2015connectome}, CPAC~\cite{craddock2013towards}, DPARSF~\cite{yan2010dparsf},
fMRIPrep~\cite{esteban2019fmriprep}) and identified the main
factors contributing to these differences. The magnitude of the highlighted
differences suggest that between-tool variability may be playing a critical
role in the reproducibility of fMRI analysis overall.

The variability resulting from differences in lower-level software
libraries (within-tool variability) has also been quantified in fMRI. The
study in~\cite{Glatard2015} mentions a low similarity between the activation clusters
produced by FSL using different versions of the GNU/Linux system, measured
by Dice coefficients ranging from 0.0 to 1.0, covering the full spectrum of
possible similarities. This variability resulted from updates in the GNU
mathematical library and can be properly simulated by introducing small
numerical perturbations on the results returned by mathematical functions~\cite{salari2021accurate}.
Here again, these observations could partly explain the differences
reported in~\cite{botvinik2020variability}.

The relationship between within- and between-tool variability are poorly
understood, but could play an important role in the construction of
multiverse study environments. Importantly, if associations exist between
these two types of variability, they may both originate to some degree from
the inherent instability of brain activity estimation from BOLD signal
variations, and shed light on the numerical confidence of results. Under
this hypothesis, small perturbations introduced by low-level software
updates could trigger effects correlated with those created by tool
variations.

This paper investigates the relationship between numerical stability -- used
as a proxy for within-tool variability -- and between-tool variability
through two main questions:
\begin{enumerate}
\item what is the relative magnitude of within-tool variability and between-tool variability, and
\item is there an association between within- and between-tool variability.
\end{enumerate}

@@

\subsection{Within-tool variability simulation with Fuzzy Libmath}

We simulated within-tool variability by introducing 
numerical noise in the analyses using
Fuzzy Libmath~\cite{salari2021accurate}, a version of the GNU
mathematical library (libmath) instrumented with Monte-Carlo arithmetic.
Monte-Carlo arithmetic simulates numerical errors
by introducing a controlled amount of noise in floating-point
operations through the following perturbation~\cite{Parker1997-qq}:

@@

We measured between-tool (BT) variability by running the pipelines
described in~\cite{bowring2019exploring} with FSL version 5.0.10, AFNI
version 18.1.09, and SPM12 version r7771 executed with GNU/Octave version
5.2. These software versions were identical to the ones used 
in~\cite{bowring2019exploring} except for SPM for which we used GNU/Octave
instead of MATLAB to enable mathematical function instrumentation using
Fuzzy Libmath. Indeed, MATLAB uses its own built-in mathematical functions,
which prevents the use of Fuzzy Libmath. In AFNI, we set the number of
threads to 7 even though AFNI executions
in~\cite{bowring2019exploring} were single-threaded. This was meant to
reduce the time overhead resulting from Fuzzy Libmath instrumentation.
% \gk{Did we verify that single-threading generally didn't lead to different
% results than 7-threading? As in, were they all ostensibly sampled from the
% same random distribution?} \ali{We verified that multithreading leads to
% different results (e.g. single-threading vs, 7-threading). However,
% single-threaded executions couldn't reproduce the original results.}
% \tristan{Fig S1 answers this comment and is refered later on}
All the analyses were conducted on the CentOS 7.3 operating system. The
computations were performed on \href{https://www.computecanada.ca}{Compute
  Canada's} Béluga cluster nodes, each with 2$\times$ Intel Gold 6148 Skylake~@~2.4~GHz
(40 cores/node) CPU and 8~GB of RAM per core. To facilitate portability and reproducibility,
we encapsulated the
above-mentioned software packages in Docker container images based on CentOS 7.3.
Although, we converted Docker containers to Singularity images to enable running on cluster nodes.

We simulated within-tool (WT) variability by running the same analyses three
times using Fuzzy Libmath with a virtual precision of $t=53$~bits for
double-precision values and $t=24$~bits for single-precision values. These
values were chosen such that the numerical perturbation simulates machine
error. The resulting samples were equally plausible estimates of
the true
% \yohan{How can you assert that when you don't have ground truth? Would it be more safe to say "plausible estimates numerical solutions"?}
% \tristan{This does not refer to the ground truth but to the true \emph{numerical} result}
numerical result at the precision used by the pipelines. Moreover, to evaluate numerical perturbations at different magnitudes,
we repeated the FSL analyses for virtual
precisions ranging from $t=1$~bit to $t=24$~bits for single-precision
and double-precision values. We also repeated the FSL analyses for virtual
precisions ranging from $t=24$~bits to $t=53$~bits for double-precision values, having
set the virtual precision to $t=24$~bits for single-precision values.

We evaluated BT variability for thresholded as well as unthresholded
group-level and subject-level t-statistics maps by computing the absolute
differences of t-statistic maps across tools. For WT, we computed the
average absolute difference across the three Fuzzy Libmath samples.
Moreover, we computed WT variability for a pair of tools as the sum of WT values for each tool.

@@

\subsection{Validation of Replication}

@@

\subsection{In the group analysis, BT variability was larger than WT variability}

Table~\ref{table:pipeline-stats} presents summary statistics for variability in the
group-level t-statistics. For each tool pair (A, B), BT variability was
significantly larger than machine error in tool A or B, in both thresholded
and unthresholded maps (Wilcoxon signed-rank test and t-test p~\textless~$10^{-5}$ for all tests).
% \gk{we don't have sufficient sample size to say that p is that small,
% so we should probably say less than $10^{-5}$ or something else we could actually
% arrive at with our number of repetitions, pipeline pairs, and samples.}
% for all tests, t-test p=0 \gk{similar comment re p value} for all tests) \camille{p is smaller than a very small p but not zero?}.
Figure~\ref{fig:unthresh-maps}-\textbf{A},\textbf{B} shows that
these global differences were confirmed regionally.
In addition, BT and WT variability appeared moderately correlated across voxels (Pearson's r
in [0.60, 0.62], p$< 10^{-5}$, Figure~\ref{fig:unthresh-maps}-\textbf{C}). 
% Interestingly, the correlation appears driven by a set of voxels exhibiting comparable BT and
% WT values located around the identity line in Figure~\ref{fig:unthresh-maps}D, which, however, did not seem to have
% any spatial consistency.

@@

\begin{figure*}[ht]
  \centering
  % \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
  \begin{subfigure}[ht]{.9\textwidth}
    \centering
    \includegraphics[width=.9\textwidth]{figures/gl-unthresh.png}
    % \includegraphics[width=0.9\textwidth]{figures/abs/gl-unthresh.png}
    %\caption{Standard deviation of thresholded t-statistics map on template surface}
  \end{subfigure}
  \caption{Unthresholded group-level differences computed between tools
    (\textbf{A}), within tools at machine error (\textbf{B}),
    and voxel-wise comparison of absolute differences (\textbf{C}). }
  \label{fig:unthresh-maps}
  % \end{minipage}}
\end{figure*}

\subsection{In subject analyses, WT variability approached BT variability in some regions}

Table~\ref{table:pipeline-stats} also presents summary statistics for
subject-level unthresholded t-statistics maps. As for group-level maps,
BT variability was consistently larger than WT variability (Wilcoxon
signed-rank test and t-test p~\textless~$10^{-5}$ for all tests).
However, Figure~\ref{fig:unthresh-maps-sbj} shows that for
some subjects, WT variability approached %and even surpassed
BT in some regions. As for the group maps, BT and WT
variability appeared moderately correlated for all subjects (r in [0.484,
    0.633], p$< 10^{-5}$ for all subjects, see Supplemental Material~\ref{sec:supp-subjects} and~\ref{sec:supp-worst-subject}).

@@

\subsection{At precision t=17~bits, WT variability approached BT variability in the group analysis}

While the previous results were obtained for machine error, we also
evaluated numerical variability across different virtual precisions for FSL
and found that the virtual precision of t=17 bits minimized the RMSE
between BT and WT in unthresholded group maps.
FSL produced unthresholded group maps with $\mu=0.483$ and $\sigma=0.410$ at this virtual precision,
which was still lower than BT variability
(Wilcoxon signed-rank test and t-test p~\textless~$10^{-5}$ for all tests).
However, Figure~\ref{fig:gnp-mni} shows that
BT and WT reached comparable magnitudes in some regions. BT and WT remained
moderately correlated at this precision (Pearson's r
in [0.53, 0.61], p$< 10^{-5}$, Figure~\ref{fig:gnp-mni}-\textbf{B}).

@@

Figure~\ref{fig:thresh-maps}-\textbf{A},\textbf{B},\textbf{C} compares BT
and WT for thresholded group maps. Thresholding is an unstable operation
that introduced variability at the edges of
active regions for both BT and WT. Except at the edges, BT remained consistently larger
than WT.
%\gk{what regions? This kind of came from nowhere}\tristan{I meant "at the edges", fixed.}
 Moreover, to measure correlation between BT and WT, we
measured WT instability and BT instability in each region of the
HCP-MMP1.0 parcellation \gk{again, it feels kind of abrupt and I'm not really sure what this section is getting at or how it differs from the previous based on these descriptions. Perhaps introduce that thresholding is common, but since it makes things discontinuous we study it through aparcellation, etc...}. The confusion matrices in
Figure~\ref{fig:thresh-maps}-\textbf{D} report these instabilities for
the 360 tested regions. The average ratio of unstable regions was 26\%
for BT and 9.2\% for WT, which confirmed that BT variability was larger than machine error.
The average Cohen's kappa score\footnote{$\kappa \leq 0$ denotes chance agreement, $-1 \leq \kappa \leq 1$}
between WT instability and BT instability was $\kappa=0.17$, indicating
a moderate agreement between WT instability and BT instability.

@@

Figure~\ref{fig:replication-diff} shows the difference in SPM and AFNI
group analyses maps between the results in~\cite{bowring2019exploring} and
our replication. Numerical perturbations of 1 ulp are likely to have been
introduced by our replication due to the use of GNU/Octave vs MATLAB for SPM
and multithreading for AFNI \camille{Would this be feasible to check?}. However, the group maps remained very similar
overall, which led us to conclude that our results correctly reproduced
the ones in~\cite{bowring2019exploring}.
\begin{figure*}[ht]
  % \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
  % \centering
  \includegraphics[width=\textwidth]{figures/replication-diffs.png}
  \caption{Differences between reproduced and original results obtained in~\cite{bowring2019exploring}
    of unthresholded group-level t-statistics for SPM (left) and AFNI (right). \camille{it looks like the highest areas of difference in AFNI are due to difference un masking maybe worth noting?}}
  \label{fig:replication-diff}
  % \end{minipage}}
\end{figure*}

>>>>

\title{Comparing software variability across and within fMRI analysis packages}

@@

\maketitle
\begin{abstract}
  Variability has been broadly observed in functional MRI analyses as a result
  of software differences
  both between and within analytic tools. However, the
  relationship between within-tool and between-tool software variabilities for a
  given analysis is unclear. We extended a previous comparison of fMRI
  analysis software libraries (namely FSL, AFNI, and SPM) and related the
  observed differences to within-tool software variability
  simulated using Monte-Carlo arithmetic. In group analyses, we found that
  between-tool software variability was consistently larger than within-tool software
  variability simulated at the magnitude of
  machine error. In subject analyses, the same within-tool software variability
  approached between-tool software variability in some regions for some subjects.
  Interestingly, within- and between-tool software variabilities appeared moderately
  correlated ($r > 0.5$) in all tested conditions. Finally, we found that
  within-tool software variability had effects of similar magnitude to between-tool
  software variability when simulated from numerical perturbations introduced at the virtual
  precision of 17 bits --- a high but plausible level of uncertainty for
  scientific computing libraries. \tristan{Revise from latest results}
  %  \gk{What does this mean? They only have
  % precision of 17, or they use data that is 17 bits?}
  %  \yohan{agree with Greg, it is unclear and a strong assertion!}
  %  \camille{It is not entirely clear to me how this relates to the previous
  %  conclusions that BT variability was consistently larger than machine
  %  error} \tristan{Better?}
   Our findings motivate the
  continued investigation of within-tool software variability in neuroimaging, and position it
  as a possible proxy for studying some of the arbitrary between-tool software variations.
\end{abstract}

@@

Recent explorations of the analytical flexibility in brain imaging across
tools, platforms, or teams, have demonstrated unexpected variability in
results, even when analyzing identical data~\cite{botvinik2020variability}. Possible explanations for
such discrepancies include methodological flexibility~\cite{carp2012plurality} and software
variability, the focus of this paper. A recommendation to address this
variability is to adopt a ``multiverse" approach that analyzes the same
dataset multiple times in different software environments, and ultimately
conclude from the resulting set of outcomes. However, the range of
analytical conditions to be included in such multiverse analyses remains
poorly defined, both because of the boundless set of tools and
configurations, and that the precise causes of software variability remain
unclear. This lack of clarity is in part because fMRI analyses depend on
complex software stacks that leverage low-level libraries provided by the
operating system (e.g., mathematical functions), general scientific
computing methods (e.g., optimization toolboxes), and specific fMRI
analysis tools (e.g., spatial image normalization methods). At each level,
conceptual and implementation differences across experiments may each
create substantial variability in the analysis outcomes.

As a result of these factors, the variability resulting from the use of
different fMRI analysis tools implementing similar analytical approaches
(between-tool software variability), or different versions of the same tool,
 can reach worrying magnitudes. For instance, the
study in~\cite{bowring2019exploring} compared the results produced by the
three main fMRI analysis toolboxes, namely SPM~\cite{penny2011statistical},
AFNI~\cite{cox1996afni} and FSL~\cite{jenkinson2012fsl}, using similar
pipelines. It reported limited similarity between the activation clusters
produced by these tools, measured by Dice coefficients ranging from 0.0 to
0.769, where 0 indicates non-overlapping
clusters and 1 means identical clusters. More recently, the work
in~\cite{Li2021.12.01.470790} also showed a low similarity between the
results produced by five different tools (ABCD~\cite{feczko2021adolescent},
CCS~\cite{xu2015connectome}, CPAC~\cite{craddock2013towards}, DPARSF~\cite{yan2010dparsf},
fMRIPrep~\cite{esteban2019fmriprep}) and identified the main
factors contributing to these differences. The magnitude of the highlighted
differences suggest that between-tool software variability may be playing a critical
role in the reproducibility of fMRI analysis overall.

The variability resulting from differences in lower-level software
libraries (within-tool software variability) has also been quantified in fMRI. The
study in~\cite{Glatard2015} mentions a low similarity between the activation clusters
produced by FSL using different versions of the GNU/Linux system, measured
by Dice coefficients ranging from 0.0 to 1.0, covering the full spectrum of
possible similarities. This variability resulted from updates in the GNU
mathematical library and can be properly simulated by introducing small
numerical perturbations on the results returned by mathematical functions~\cite{salari2021accurate}.
Here again, these observations could partly explain the differences
reported in~\cite{botvinik2020variability}.

The relationship between within- and between-tool software variability are poorly
understood, but could play an important role in the construction of
multiverse study environments. Importantly, if associations exist between
these two types of variability, they may both originate to some degree from
the inherent instability of brain activity estimation from BOLD signal
variations, and shed light on the numerical confidence of results. Under
this hypothesis, small perturbations introduced by low-level software
updates could trigger effects correlated with those created by tool
variations.

This paper investigates the relationship between numerical stability --- used
as a proxy for within-tool software variability --- and between-tool software variability
through two main questions:
\begin{enumerate}
\item what is the relative magnitude of within- and between-tool software variability, and
\item is there an association between within- and between-tool software variability.
\end{enumerate}

@@

\subsection{Within-tool software variability simulation with Fuzzy Libmath}

We simulated within-tool software variability by introducing 
numerical noise in the analyses using
Fuzzy Libmath~\cite{salari2021accurate}, a version of the GNU
mathematical library (libmath) instrumented with Monte-Carlo arithmetic.
Monte-Carlo arithmetic simulates numerical errors
by introducing a controlled amount of noise in floating-point
operations through the following perturbation~\cite{Parker1997-qq}:

@@

We measured between-tool software variability (BT) by running the pipelines
described in~\cite{bowring2019exploring} with FSL version 5.0.10, AFNI
version 18.1.09, and SPM12 version r7771 executed with GNU/Octave version
5.2. These software versions were identical to the ones used 
in~\cite{bowring2019exploring} except for SPM for which we used GNU/Octave
instead of MATLAB to enable mathematical function instrumentation using
Fuzzy Libmath. Indeed, MATLAB uses its own built-in mathematical functions,
which prevents the use of Fuzzy Libmath. In AFNI, we set the number of
threads to 7 even though AFNI executions
in~\cite{bowring2019exploring} were single-threaded. This was meant to
reduce the time overhead resulting from Fuzzy Libmath instrumentation.
% \gk{Did we verify that single-threading generally didn't lead to different
% results than 7-threading? As in, were they all ostensibly sampled from the
% same random distribution?} \ali{We verified that multithreading leads to
% different results (e.g. single-threading vs, 7-threading). However,
% single-threaded executions couldn't reproduce the original results.}
% \tristan{Fig S1 answers this comment and is refered later on}
All the analyses were conducted on the CentOS 7.3 operating system. The
computations were performed on \href{https://www.computecanada.ca}{Compute
  Canada's} Béluga cluster nodes, each with 2$\times$ Intel Gold 6148 Skylake~@~2.4~GHz
(40 cores/node) CPU and 8~GB of RAM per core. To facilitate portability and reproducibility,
we encapsulated the
above-mentioned software packages in Docker container images based on CentOS 7.3
which we converted to Singularity images to enable running on cluster nodes.

We simulated within-tool software variability (WT) by running the same analyses three
times using Fuzzy Libmath with a virtual precision of $t=53$~bits for
double-precision values and $t=24$~bits for single-precision values. These
values were chosen such that the numerical perturbation simulates machine
error. The resulting samples are equally plausible estimates of
the true
% \yohan{How can you assert that when you don't have ground truth? Would it be more safe to say "plausible estimates numerical solutions"?}
% \tristan{This does not refer to the ground truth but to the true \emph{numerical} result}
numerical result at the precision used by the pipelines. Moreover, to evaluate numerical perturbations at different magnitudes,
we repeated the FSL analyses for virtual
precisions ranging from $t=1$~bit to $t=24$~bits for single-precision
and double-precision values. We also repeated the FSL analyses for virtual
precisions ranging from $t=24$~bits to $t=53$~bits for double-precision values, having
set the virtual precision to $t=24$~bits for single-precision values.

We evaluated BT for thresholded as well as unthresholded
group-level and subject-level t-statistics maps by computing the absolute
differences of t-statistic maps across tools. For WT, we computed the
average absolute difference across the three Fuzzy Libmath samples.
Moreover, we computed WT variability for a pair of tools as the sum of WT values for each tool.

@@

\subsection{Validation of replication}

@@

\subsection{In the group analysis, BT was larger than WT}

Table~\ref{table:pipeline-stats} presents summary statistics for variability in the
group-level t-statistics. For each tool pair (A, B), BT was
significantly larger than machine error in tool A or B, in both thresholded
and unthresholded maps (Wilcoxon signed-rank test and t-test p~\textless~$10^{-5}$ for all tests).
% \gk{we don't have sufficient sample size to say that p is that small,
% so we should probably say less than $10^{-5}$ or something else we could actually
% arrive at with our number of repetitions, pipeline pairs, and samples.}
% for all tests, t-test p=0 \gk{similar comment re p value} for all tests) \camille{p is smaller than a very small p but not zero?}.
These global differences were confirmed by Bland-Altman plots showing a
clear dominance of BT over WT
(Figure~\ref{fig:unthresh-maps}-\textbf{A},\textbf{B}).
In addition, BT and WT appeared moderately correlated across voxels (Pearson's r
in [0.60, 0.62], p$< 10^{-5}$, Figure~\ref{fig:unthresh-maps}-\textbf{C}). 
% Interestingly, the correlation appears driven by a set of voxels exhibiting comparable BT and
% WT values located around the identity line in Figure~\ref{fig:unthresh-maps}D, which, however, did not seem to have
% any spatial consistency.

@@

\begin{figure*}[ht]
  \centering
  % \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
  \begin{subfigure}[ht]{.9\textwidth}
    \centering
    \includegraphics[width=.9\textwidth]{figures/gl-unthresh.png}
    % \includegraphics[width=0.9\textwidth]{figures/abs/gl-unthresh.png}
    %\caption{Standard deviation of thresholded t-statistics map on template surface}
  \end{subfigure}
  \caption{\textbf{A} and \textbf{B}: Bland-Altman plots comparing group-level differences computed between tools
    (\textbf{A}) and within tools at machine error (\textbf{B}). \textbf{C}: voxel-wise comparison of absolute differences.}
  \label{fig:unthresh-maps}
  % \end{minipage}}
\end{figure*}

\subsection{In subject analyses, WT approached BT for some subjects}

Table~\ref{table:pipeline-stats} also presents summary statistics for
subject-level unthresholded t-statistics maps. As for group-level maps,
BT was consistently larger than WT (Wilcoxon
signed-rank test and t-test p~\textless~$10^{-5}$ for all tests).
However, for
some subjects and for AFNI, WT approached 
BT in some regions (Figure~\ref{fig:unthresh-maps-sbj}). As for the group maps, BT and WT
 appeared moderately correlated for all subjects (r in [0.484,
    0.633], p$< 10^{-5}$ for all subjects, see Supplemental Material~\ref{sec:supp-subjects} and~\ref{sec:supp-worst-subject}).

@@

\subsection{At precision t=17~bits and in FSL, WT approached BT in the group analysis}
\tristan{We cannot say that from the data that we have.}
\tristan{Discuss subject-level BA plots.}
While the previous results were obtained by simulating WT with numerical perturbations 
at the magnitude of machine error, we also
evaluated numerical variability across different virtual precisions for FSL
and found that the virtual precision of t=17 bits minimized the RMSE
between BT and WT in unthresholded group maps.
FSL produced unthresholded group maps with $\mu=0.483$ and $\sigma=0.410$ at this virtual precision,
which was still lower than BT variability
(Wilcoxon signed-rank test and t-test p~\textless~$10^{-5}$ for all tests).
However, Figure~\ref{fig:gnp-mni} shows that
BT and WT reached comparable magnitudes in some regions. BT and WT remained
moderately correlated at this precision (Pearson's r
in [0.53, 0.61], p$< 10^{-5}$, Figure~\ref{fig:gnp-mni}-\textbf{B}).

@@

We also compared BT and WT in thresholded maps since these maps are commonly used instead of unthresholded ones 
to conclude on the activation of specific regions. Thresholding is an unstable operation
that introduced variability at the edges of
active regions for both BT and WT. Except at the edges, BT remained consistently larger
than WT (Figure~\ref{fig:thresh-maps}-\textbf{A},\textbf{B},\textbf{C} and Table~\ref{table:pipeline-stats}).

Moreover, to compare the effects of BT and WT on the detection of activated
regions, we measured WT instability and BT instability in each region of
the HCP-MMP1.0 parcellation. The confusion matrices in
Figure~\ref{fig:thresh-maps}-\textbf{D} report these instabilities for the
360 tested regions. The average ratio of unstable regions was 26\% for BT
and 9.2\% for WT, which confirmed that BT was larger than
WT even in thresholded maps.

Finally, we measured agreement between BT and WT from the confusion
matrices since interpreting the correlation of thresholded maps is
difficult due to the discontinuity introduced by thresholding. 
The average Cohen's kappa score\footnote{$\kappa \leq 0$ denotes chance agreement, $-1 \leq \kappa \leq 1$}
computed from the confusion matrices between WT instability and BT instability was $\kappa=0.17$, indicating
a moderate agreement between WT instability and BT instability consistent with the correlations observed in 
unthresholded maps.

% \gk{again, it feels kind of abrupt and I'm not really sure what this
% section is getting at or how it differs from the previous based on these
% descriptions. Perhaps introduce that thresholding is common, but since it
% makes things discontinuous we study it through aparcellation, etc...}.
% \tristan{better now?}

@@

Figure~\ref{fig:replication-diff} shows the difference in SPM and AFNI
group analyses maps between the results in~\cite{bowring2019exploring} and
our replication. Numerical perturbations of 1 ulp are likely to have been
introduced by our replication due to the use of GNU/Octave vs MATLAB for SPM
and multithreading for AFNI.
 \camille{Would this be feasible to check?}
 \tristan{Ali, could you answer that?}
  However, the group maps remained very similar
overall, which led us to conclude that our results correctly reproduced
the ones in~\cite{bowring2019exploring}.
\begin{figure*}[ht]
  % \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
  % \centering
  \includegraphics[width=\textwidth]{figures/replication-diffs.png}
  \caption{Differences between reproduced and original results obtained in~\cite{bowring2019exploring}
    of unthresholded group-level t-statistics for SPM (left) and AFNI
    (right). The highest areas of difference in AFNI seem to be due to
    differences in brain masks.}
  \label{fig:replication-diff}
  % \end{minipage}}
\end{figure*}
